Reproducibility in Plant Pathology

### 2019-01-02 README.rmd
Update pkgdown site
Update README file

> Sparks, A.H., Del Ponte, E.M., Everhart, S., Foster, Z.S.L., Grünwald, N., (`r format(Sys.Date(), "%Y")`). _Compendium of R code and data for 'Status and Best Practices for Reproducible Research In Plant Pathology'_. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/10.5281/zenodo.1250665>

@@

Or you can install this compendium as an R package, Reproducibility.in.Plant.Pathology, from GitHub with:
```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("adamhsparks/Reproducibility_in_Plant_Pathology")
```

>>>>

> Sparks, A.H., Del Ponte, E.M., Everhart, S., Foster, Z.S.L., Grünwald, N. (`r format(Sys.Date(), "%Y")`). _Compendium of R code and data for 'Status and Best Practices for Reproducible Research In Plant Pathology'_. Accessed `r format(Sys.Date(), "%d %b %Y")`. Online at <https://doi.org/10.5281/zenodo.1250665>

@@

Or you can install this compendium as an R package, Reproducibility.in.Plant.Pathology, from GitHub with:
```{r gh-installation, eval = FALSE}
if (!require("remotes")) install.packages("remotes")
remotes::install_github("openplantpathology/Reproducibility_in_Plant_Pathology")
```
